\tool: Programmable and Efficient Secure Two-Party Computation for Machine Learning

### 2018-08-07 ndss/eval.tex
minor

\noindent\textbf{Scalability.}  To
illustrate the scalability of partitioning, we evaluate a
sequence of DNNs with and without partitioning in~\figureref{partitioning}.
All layers are identical and partitioning places each layer in a separate stage. 
For DNNs with up to 4  layers, the performance, with and without partitioning, is almost identical and the lines overlap, thereby
illustrating that partitioning does not cause any noticeable performance overheads.
Memory issues start showing up in the non-partitioned implementation of the 5 layer DNN and it is slower.
Performance degrades rapidly thereafter and
DNNs with 6 or more layers fail to execute (terminate with a ``bus error").
However, the partitioned implementation scales well to even these large DNNs.

>>>>

\noindent\textbf{Scalability.}  To
illustrate the scalability of partitioning, we evaluate a
sequence of DNNs with and without partitioning in~\figureref{partitioning}.
All layers are identical and partitioning places each layer in a separate stage. 
For DNNs with up to 4  layers, the performance, with and without partitioning, is almost identical and the lines overlap, thereby
illustrating that partitioning does not cause any noticeable performance overheads.
Memory issues start showing up in the non-partitioned implementation of the 5 layer DNN and it is slower.
In particular, the circuit for this DNN does not fit in RAM and uses swap space.
Performance degrades rapidly thereafter: executing the 5 layer DNN and half operations of the sixth layer incurs a 2x slowdown.
DNNs with 6 or more layers fail to execute (terminate with a ``bus error").
However, the partitioned implementation scales well to even these large DNNs.

### 2018-08-07 ndss/intro.tex
minor

\subsubsection{Scalability (secure code partitioning)} \mpc tools
often do not scale to large functionalities. The reason is that
most \mpc implementations use a circuit-like representation as an
intermediate language. Hence, the largest compute that can be done
securely is upper-bounded by the largest circuit that can fit in the
machine memory\footnote{Using swap and
disk space is feasible but it causes huge slowdown.}. This is a
show-stopper for applications like secure machine learning, secure
prediction, etc. that operate on large data.
%\aseem{Can we
%cite something here to support this claim?}
\tool addresses the scalability concern using a novel technique that
we call secure code partitioning (or partitioning in short). At
a high level, we decompose the original program into a sequence of small
sub-programs, which are then sequentially processed by \tool, while
appropriately threading the intermediate outputs
along. While this
addresses the scalability concern (i.e., the circuit
sizes of the sub-programs are now small enough to fit in the memory),
we still have to address
the security risk of revealing the intermediate outputs. \tool comes
to the rescue; it automatically inserts the required instrumentation
to ensure security of these intermediate outputs (\sectionref{pipe}). As
we show in our
evaluation, partitioning allows us to program large applications
in \tool. 
%\aseem{What about the differences from Yao pipelining? Worth
%adding here that it is a backend-agnostic technique?}

>>>>

\subsubsection{Scalability (secure code partitioning)} \mpc tools
often do not scale to large functionalities. The reason is that
most \mpc implementations use a circuit-like representation as an
intermediate language. Hence, the largest compute that can be done
securely is upper-bounded by the largest circuit that can fit in the
machine memory\footnote{Using swap and
disk space is feasible but it causes huge slowdown ~\figureref{partitioning}).}. This is a
show-stopper for applications like secure machine learning, secure
prediction, etc. that operate on large data.
%\aseem{Can we
%cite something here to support this claim?}
\tool addresses the scalability concern using a novel technique that
we call secure code partitioning (or partitioning in short). At
a high level, we decompose the original program into a sequence of small
sub-programs, which are then sequentially processed by \tool, while
appropriately threading the intermediate outputs
along. While this
addresses the scalability concern (i.e., the circuit
sizes of the sub-programs are now small enough to fit in the memory),
we still have to address
the security risk of revealing the intermediate outputs. \tool comes
to the rescue; it automatically inserts the required instrumentation
to ensure security of these intermediate outputs (\sectionref{pipe}). As
we show in our
evaluation, partitioning allows us to program large applications
in \tool. 
%\aseem{What about the differences from Yao pipelining? Worth
%adding here that it is a backend-agnostic technique?}
